---
title: "VSL Pre-/Post-eval summary"
author: "David Kent (dk657)"
date: "June 13, 2017"
output: 
  html_document:
    toc: true
---


```{r load, include=FALSE}
library(knitr)
library(lsmeans)
source("plot_all_defects.R")
```

## Radial plots of incorrect marks
```{r fig.width=12,fig.height=7}
for( i in unique(incorrect_marks$Defect) ) {
  incorrect_marks %>%
    filter(Defect==i) %>%
    mutate(incorrect_defect=ifelse(incorrect_defect==i,
                                   paste(i,"\n+ Other"),
                                   incorrect_defect)) %>%
    mutate(incorrect_defect=gsub("_","\n",incorrect_defect)) -> temp
  tests %>% 
    filter(Defect==i) %>% 
    summarize(n_total=n(),
              n_incorrect=n() - sum(correct)) -> n_summary
  
  ggplot(temp, aes(x=incorrect_defect,
             y=num_marked,
             color=Pre_Post,
             fill=Pre_Post)) +
    theme_bw() +
    labs(title=paste(i,"Samples"),
         x="Marked Defect",
         y="Number Marked",
         fill="Pre- or Post-Test",
         color="Pre- or Post-Test",
         caption=paste("Of",
                       n_summary$n_total,
                       i,
                       "samples,",
                       n_summary$n_incorrect,
                       "were marked incorrectly; a single sample can be marked multiple defects")) +
    #theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)) +
    scale_y_continuous(breaks=1:(incorrect_marks %>% filter(Defect==i) %>% select(num_marked) %>% max())) +
    geom_bar(stat="identity", position="dodge") +
    coord_polar() +
    facet_grid(~Initial_Text) -> g
  print(g)
  #ggsave(filename = paste(i,".pdf",sep=""),
  #       plot = g,
  #       device= "pdf",
  #       width=11,
  #       height=8.5,
  #       units = "in",
  #       path = "pdfs")
}
```

## Standard plots of incorrect marks
```{r fig.width=12,fig.height=7}
for( i in unique(incorrect_marks$Defect) ) {
  ggplot(incorrect_marks %>%
           filter(Defect==i) %>%
           rename(),
         aes(x=incorrect_defect,
             y=num_marked,
             color=Pre_Post,
             fill=Pre_Post)) +
    theme_bw() +
    labs(title=paste(i,"Samples"),
         x="Marked Defect",
         y="Number Marked",
         fill="Pre- or Post-Test",
         color="Pre- or Post-Test") +
    theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)) +
    scale_y_continuous(breaks=1:(incorrect_marks %>% filter(Defect==i) %>% select(num_marked) %>% max())) +
    geom_bar(stat="identity", position="dodge") +
    #coord_polar() +
    facet_grid(~Initial_Text) -> g
  print(g)
}
```

# Statistics

In the following, we fit a generalized (logistic) linear model. Each observation
consists of one prepared sample, and is regarded as a "success" if the prepared
defect was marked appropriately by the panelist, and a "failure" otherwise. We
use a three-way interaction of "Pre_Post" (whether the test was occurring before
or after a training session), "initial" (whether this test was associated with 
the panelist's first training session), and "Defect" (what the prepared defect
was), and associated two-way interactions and main effects. Milk_Type (skim or
2%) was a included as a blocking effect.

We use the least-squares means estimates from this model to visualize andassess
the contrasts between Pre/Post and Initial/Re-training effects.

### Fit model; compute least-square means
```{r}
tests %>%
  filter(!(Pre_Post=="Post" & Defect=="Fruity_Fermented" & initial=="Re-training")) %>%
  glm(correct~initial*Pre_Post*Defect+Milk_Type,
      data=.,
      family="binomial") -> m

lsmeans(object=m,~initial+Defect+Pre_Post) %>%
  summary() %>%
  data.frame() -> estimated_for_plot

estimated_for_plot$lsmean[estimated_for_plot$Pre_Post=="Post" &
                            estimated_for_plot$Defect=="Fruity_Fermented" &
                            estimated_for_plot$initial=="Re-training"] <- Inf
```

### Plot of changes from before and after training
```{r fig.width=12,fig.height=7}
estimated_for_plot %>%
  ggplot(aes(x=Defect,y=plogis(lsmean))) +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)) +
  geom_path(arrow = arrow(length=unit(0.30,"cm"), ends="last", type = "closed"),
            position=position_dodge(width=1)) +
  geom_point(aes(color=Pre_Post)) +
  labs(x="Defect",y="Percent Correct",color="Pre- or post-training") +
  facet_grid(.~initial)
```

### Plot of changes from before and after training (log-odds)
```{r fig.width=12,fig.height=7}
estimated_for_plot %>%
  ggplot(aes(x=Defect,y=lsmean)) +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)) +
  geom_path(arrow = arrow(length=unit(0.30,"cm"), ends="last", type = "closed"),
            position=position_dodge(width=1)) +
  geom_point(aes(color=Pre_Post)) +
  labs(x="Defect",y="Log-odds correct",color="Pre- or post-training") +
  facet_grid(.~initial)
```

### Plot comparing Initial and Re-training
```{r fig.width=12,fig.height=7}
estimated_for_plot %>%
  ggplot(aes(x=Defect,y=plogis(lsmean))) +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)) +
  geom_path(arrow = arrow(length=unit(0.30,"cm"), ends="last", type = "closed"),
            position=position_dodge(width=1)) +
  geom_point(aes(color=initial)) +
  labs(x="Defect",y="Percent Correct",color="Initial or Re-training") +
  facet_grid(.~Pre_Post)
```

### Pairwise comparison between Pre/Post within Defect and Initial/Re-training
```{r results="asis"}
lsmeans(object=m,pairwise~Pre_Post|Defect+initial,adjust="none") %>%
  summary() -> lsm_pre_post 

lsm_pre_post$contrasts %>%
  data.frame() -> pre_post_contrasts

pre_post_contrasts$p.adj <- p.adjust(pre_post_contrasts$p.value,method = "holm")

pre_post_contrasts$signif <- pre_post_contrasts$p.adj < 0.05

kable(pre_post_contrasts)
```

### Pairwise comparison between Initial/Re-training within Defect and Pre/Post
```{r}
lsmeans(object=m,pairwise~initial|Defect+Pre_Post,adjust="none") %>%
  summary() -> lsm_initial

lsm_initial$contrasts %>%
  data.frame() -> initial_contrasts

initial_contrasts$p.adj <- p.adjust(initial_contrasts$p.value,method = "holm")

initial_contrasts$signif <- initial_contrasts$p.adj < 0.05

kable(initial_contrasts)
```